Self-Supervised Learning of Generalized Policies in adversarial domains

### 2021-05-28 doc/paper/paper.tex
changes in doc

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
(A) Num[cell-has-martian] [k=1]
(B) Bool[cell-has-target_martian] [k=1]
(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[cell-has-martian] [k=1]:
  (B) Bool[cell-has-target_martian] [k=1]:
  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
  absolute horizontal distance between agent and target martian
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  m..m # m..M # m..M # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  m..M # m... # m... # m..M # m... # m... # .m.. # .M.. # .M.. # M... # M... # .... #
  .... # .... # .... # m... # M... # M... # .M.. # .... # .... # .... # .... # .... #
  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  ..A. # ...A # ..A. # ..A. # ...A # ..A. # ..A. # .A.. # ..A. # ..A. # .A.. # A... #
  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]:
  the column of the agent is adjacent to the column of the adversary

  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]:
  the row of the agent is adjacent to the row of the adversary

  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]:
  absolute vertical distance between agent and adversary

  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]:
  absolute horizontal distance between agent and adversary
\end{Verbatim}

\subsubsection{Policy (with no fixed action space)}

\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND D>0 AND C=0 -> {A ↑, B ↑, C ↑, D ↓}, {A ·, B ↑, C ↑, D ↓}
  2. A=0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ↓}, {A ↑, B ↑, C ↓, D ↓},
                                    {A ·, B ·, C ↓, D ↓}, {A ↑, B ·, C ↓, D ↓}
  3. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ↓, C ↓, D ↓}, {A ↑, B ↓, C ↓, D ↓}
  4. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, B ·, C ↓, D ↓}, {A ↓, B ↑, C ↓, D ↓}
  5. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, B ·, C ↓, D ↑}, {A ↑, B ↑, C ↓, D ↑}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]:
  the column of the agent is adjacent to the column of the adversary

  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]:
  the row of the agent is adjacent to the row of the adversary

  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]:
  absolute vertical distance between agent and adversary

  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]:
  absolute horizontal distance between agent and adversary
\end{Verbatim}

\subsubsection{Policy (with no fixed action space)}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  2. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ·, C ·, D ↓}
  3. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ·, C ·, D ↓}, {A ↑, B ·, C ·, D ↓}
  4. B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  5. A=0 AND D>0 AND C>0 -> {A ↑, B ·, C ·, D ↓}
  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, B ·, C ↓, D ·}, {A ·, B ↑, C ↓, D ·}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]:
  number of tokens with a token immediately to the left of it

  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]:
  number of tokens with a token immediately to the leftdown of it

  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]:
  number of tokens with a token immediately to the rightdown of it

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A>0 AND B>0 AND C>0 -> {A ·, B ↓, C ↓}
  2. B>0 AND C>0 -> {A ·, B ↓, C ↓}

@@

In this domain the agent has to pick up a missed pet $p$ and take it to a certain location, the destination $D$. The pet has the option on its turn to escape from its captor to any of the cells adjacent to it. The goal is defined by the agent in a cell adjacent to the destination while carrying the pet. The agent has two actions per turn and the adversary one. The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.  The set of possile actions for the pet consist in escape to one of the adjacent cells to the agent, i.e. at most eight possible actions depending on the position of the agent in the grid. The pet can not escape to the delivey point.

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Atom[holding_pet] [k=1]:
  the agent is holding the pet

  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destination))] [k=5]:
  the destination is adjacent to the agent

  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]:
  manhattan distance between agent and destination

  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]:
  manhattan distance between agent and pet
\end{Verbatim}

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ·}
  2. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ↓}, {A ·, B ·, C ↑, D ↓},
                                    {A ↑, B ·, C ·, D ↑}, {A ·, B ·, C ·, D ↓}
  3. A>0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↓, D ·}
  4. A=0 AND B>0 AND C>0 AND D>0 -> {A ·, B ↓, C ↑, D ↓}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
  (B) Bool[And(col-has-AGENT,Exists(adjacent_col,col-has-TARGET))] [k=5]
  (C) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]

>>>>

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
(A) Num[cell-has-martian] [k=1]
(B) Bool[cell-has-target_martian] [k=1]
(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[cell-has-martian] [k=1]
  (B) Bool[cell-has-target_martian] [k=1]
  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
  absolute horizontal distance between agent and target martian
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  m..m # m..M # m..M # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  m..M # m... # m... # m..M # m... # m... # .m.. # .M.. # .M.. # M... # M... # .... #
  .... # .... # .... # m... # M... # M... # .M.. # .... # .... # .... # .... # .... #
  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  ..A. # ...A # ..A. # ..A. # ...A # ..A. # ..A. # .A.. # ..A. # ..A. # .A.. # A... #
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
\end{Verbatim}

\subsubsection{Feature Descrition}
$A$. The column of the agent is adjacent to the column of the adversary\\
$B$. The row of the agent is adjacent to the row of the adversary\\
$C$. Absolute vertical distance between agent and adversary\\
$D$. Absolute horizontal distance between agent and adversary
\subsubsection{Policy}

\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND D>0 AND C=0 -> {B ↑, C ↑, D ↓}
  2. A=0 AND B=0 AND D>0 AND C>0 -> {C ↓, D ↓}
  3. A=0 AND B>0 AND D>0 AND C>0 -> {B ↓, C ↓, D ↓}
  4. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, C ↓, D ↓}
  5. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, C ↓, D ↑}
\end{Verbatim}

\subsubsection{Policy Description}
According to rule three, if the agent is in the row adjacent to the adversary, it is good to stand in the same row as him. Following the rule four if the agent is in the column adjacent to the opponent it is good to be in the same column. According to rule three, if the agent is in the row adjacent to the adversary, it is good to stand in the same row as him.

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
\end{Verbatim}

\subsubsection{Feature Descrition}
$A$. The column of the agent is adjacent to the column of the adversary\\
$B$. The row of the agent is adjacent to the row of the adversary\\
$C$. Absolute vertical distance between agent and adversary\\
$D$. Absolute horizontal distance between agent and adversary

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND C>0 -> {A ·, C ↓, D ·}
  2. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ·, C ·, D ↓}
  3. A=0 AND B=0 AND D>0 AND C=0 -> {B ·, C ·, D ↓}
  4. B=0 AND D>0 AND C>0 -> {A ·, C ↓, D ·}
  5. A=0 AND D>0 AND C>0 -> {A ↑, B ·, C ·, D ↓}
  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, C ↓, D ·}
  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, C ↓, D ·}
\end{Verbatim}

\subsubsection{Policy Description}
According to rule two, if the agent is in the opponent's adjacent row, it is good to reduce the distance between them without moving from the adjacent row. Rule six is the same as 2 but with the column.

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]
  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]
  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]
\end{Verbatim}

\subsubsection{Feature Descrition}
$A$. Number of tokens with a token immediately to the left of it\\
$B$. Number of tokens with a token immediately to the leftdown of it\\
$C$. Number of tokens with a token immediately to the rightdown of it\\

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. B>0 AND C>0 -> {A ·, B ↓, C ↓}
\end{Verbatim}

\subsubsection{Policy Description}
The policy can be interpreted as leaving the two token stacks with the same number of tokens. This is done by decreasing the number of tokens that have a token to their leftdown or rightdown without decreasing the number of tokens with a token next to them.

@@

In this domain the agent has to pick up a missed pet $p$ and take it to a certain location, the destination $D$. The pet has the option on its turn to escape from its captor to any of the cells adjacent to it. The goal is defined by the agent in a cell adjacent to the destination while carrying the pet. The agent has two actions per turn and the adversary one. The set of possile actions for the agent is ~\{$pick$, $rightup$, $rightdown$, $leftdown$, $leftup\}$. The agent to pick up the pet has to execute the $pick$ action or move to the same cell where the pet is located. The set of possile actions for the pet consist in escape to one of the adjacent cells to the agent, i.e. at most eight possible actions depending on the position of the agent in the grid. The pet can not escape to the delivey point.

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Atom[holding_pet] [k=1]
  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destination))] [k=5]
  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]
  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]
\end{Verbatim}

\subsubsection{Feature Descrition}
$A$. The agent is holding the pet\\
$B$. The destination is adjacent to the agent\\
$C$. Manhattan distance between agent and destination\\
$D$. Manhattan distance between agent and pet

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ·}
  2. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ↓},
                                    {A ·, B ·, C ↑, D ↓},
                                    {A ↑, B ·, C ·, D ↑},
                                    {A ·, B ·, C ·, D ↓}
  3. A>0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↓, D ·}
  4. A=0 AND B>0 AND C>0 AND D>0 -> {A ·, B ↓, C ↑, D ↓}
\end{Verbatim}

\subsubsection{Policy Description}
According to the third rule, if the agent has the pet, it is good to move towards the destination. According to the fourth rule of the policy, if the agent does not have the pet, it is good to increase the distance to the destination and decrease the distance to the pet. Finally, according to the second rule, it is good to take the pet if you have the possibility, and if not, it is good to decrease the distance between the agent and the pet.

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
  (B) Bool[And(col-has-AGENT,Exists(adjacent_col,col-has-TARGET))] [k=5]
  (C) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
\end{Verbatim}
